Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-27 paper.qmd
Added error plot

@@

@@

>>>>

umap_data_two_curvy2_with_hb_id <- hb_obj_two_curvy2$data_hb_id
df_all_two_curvy2 <- dplyr::bind_cols(training_data_two_curvy, umap_data_two_curvy2_with_hb_id)
df_bin_two_curvy2 <- avg_highd_data(data = df_all_two_curvy2, col_start = "x")

@@

training_data_two_curvy <- training_data_two_curvy |>
  mutate(ID = row_number())

## Compute error
error_df_two_curvy_abs <- augment(
  df_bin_centroids = df_bin_centroids2,
  df_bin = df_bin_two_curvy2,
  training_data = training_data_two_curvy,
  newdata = NULL,
  type_NLDR = "UMAP",
  col_start = "x")

error_df_two_curvy_abs <- error_df_two_curvy_abs |>
  mutate(sqrt_row_wise_abs_error = sqrt(row_wise_abs_error))

error_df_two_curvy_abs <- error_df_two_curvy_abs |>
  bind_cols(umap_two_curvy_scaled |>
              select(-ID))

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "Light Grays") +
  coord_equal()

@@

```{r}
#| label: fig-p-d-error-in-2d-two-curvy
#| fig-cap: "error"
#| out-height: 30%
#| fig-pos: H

error_plot_two_curvy
```
